---
title: "Socioenvironmental"
---

A look into a socioenvironmental relationship involving environmental protection and gender.  

In this simple analysis, I am examining the proprotion of people who support environmental protection by gender.  The data being applied was acquired via GSS information.

Hypothesis: There is a significant difference between women and men's views on environmental protection.
Null hypothesis: There is not a significant difference between women and men's views on environmental protection.  

Analysis by Bar Graph and Table
```{r}
barplot(as.matrix(envlove), main="Is There Enough Environmental Protection", ylab = "Number of Individuals", xlab = "Viewpoint", cex.lab = 1, cex.main = 1.2, beside=TRUE, col = c("cornflowerblue", "cornsilk1"))
```

```{r}
envlove
```

The bar chart and table provide data that is consistent with the hypothesis that there exists a gendered difference on the views people have towards environmental protection.  Of the respondents who feel more should be done to protect the environment, 64% are female and 34% are male.  The equivalent percentages of 64% female and 34% male appear between respondents who feel enough action is being taken to protect the environment.             

Chisq Test
```{r}
envgender <- table(gss$sex, gss$natenvir)
chisq.test(envgender)

```

The chisq test reveals that there is a significant difference between the views females and males hold towards environmental protection.  With the p-value of 0.0002125, the null hypothesis is rejected.  
