---
title: "Socioenvironmental"
---

A look into a socioenvironmental relationship involving environmental protection and gender.  

In this simple analysis, I am examining the proprotion of people who support environmental protection by gender.  The data being applied was acquired via GSS information.

Hypothesis: There is a significant difference between women and men's views on environmental protection.
Null hypothesis: There is not a significant difference between women and men's views on environmental protection.  

Analysis by Bar Graph and Table
```{r}
barplot(as.matrix(envlove), main="Is There Enough Environmental Protection", ylab = "Number of Individuals", xlab = "Viewpoint", cex.lab = 1, cex.main = 1.2, beside=TRUE, col = c("cornflowerblue", "cornsilk1"))
```

```{r}
envlove
```

The bar chart and table provide data that is consistent with the hypothesis that there exists a gendered difference on the views people have towards environmental protection.  Of the respondents who feel more should be done to protect the environment, 64% are female and 34% are male.  The equivalent percentages of 64% female and 34% male appear between respondents who feel enough action is being taken to protect the environment.             

Chisq Test
```{r}
envgender <- table(gss$sex, gss$natenvir)
chisq.test(envgender)

```

The chisq test reveals that there is a significant difference between the views females and males hold towards environmental protection.  With the p-value of 0.0002125, the null hypothesis is rejected.  

In this examination, there is no evidence that can be used to explain the gendered difference of opinions.  For further analysis, surveys and in-depth interviews should be conducted with the respondents to support this simple statistical analysis.  

Additional R-code used to perform this evaluation
```{r}
gss <- read_sav("GSS2016.sav")
Too_little<-gss$sex[gss$natenvir==1] 
About_right<-gss$sex[gss$natenvir==2] 
Dont_know<-gss$sex[gss$natenvir==3] 
envlove <-structure(list(Too_little=table(Too_little), About_right=table(About_right), Dont_know=table(Dont_know)), Names=c("Too_little", "About_right", "Too_much"), class="data.frame", row.names=c("Male", "Female"))

```

Thank you for making time to see this page!  
